\documentclass[helvetica,english,nologo,notitle,nototpages,bigfont]{europasscv}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{natbib}
\usepackage{bibentry}

\renewcommand{\baselinestretch}{1.3}

\ecvname{Ashik Salim}
\ecvaddress{Kochi, Kerala, India}
\ecvmobile{+91 9995228803}
\ecvemail{ashikns@gmail.com}
\ecvlinkedinpage{linkedin.com/in/ashikns}
\ecvgithubpage{github.com/ashikns}
\ecvgender{Male}
\ecvdateofbirth{3 February 1992}
\ecvnationality{Indian}

\begin{document}
\selectlanguage{english}

\begin{europasscv}
\ecvpersonalinfo[10pt]

\vspace{8pt}
\ecvblueitem[10pt]{CAREER SUMMARY}{Developer in immersive experiences for 3+ years, primarily working on Microsoft’s Mixed Reality platform using Unity3D.}

\vspace{8pt}
\ecvsection{Work experience}

\ecvtitle[12pt]{Sept 2014 - Present}{Software Engineer}
\ecvitem[1.5pt]{}{Valorem, Kochi}

\vspace{4pt}

\ecvitem{Achievements} {
	\begin{ecvitemize}
		\item Developed native plugin for Unity3D written in C++ which achieved high performance video decoding and interoperability with WebRTC libraries.
		\item Developed a custom codec for encoding and transmission of depth data from Kinect over a traditional video stream.
		\item Ported WebRTC implementation by Google to the UWP platform, with focus on maintaining compatibility with code and build systems used by upstream.
		\item Developed a hardware decoder for H264 codec using DirectX that works with WebRTC and runs on HoloLens.
		\item Developed a system to parse, filter and store positional data of flights from a web api and accurately animate 3D representational objects in a scale to world 3D space based on this data, while maintaining strict chronological accuracy.
		\item Developed a solution to synchronize 3D coordinate space between HoloLens and Kinect allowing them to manipulate 3D objects in a shared space.
		\item Developed a real-time procedural terrain mesh generator using Bing maps api, combining both satellite image overlay and height maps.
	\end{ecvitemize}
}

\vspace{5pt}

\ecvitem{Projects} {
	\begin{ecvitemize}
		\item HoloBeam – 3D Telepresence application that captures color and depth information from Kinect, transmits it over the internet and recreates it as a hologram on the remote end. Received invitation from Microsoft to showcase at \ecvhighlight{CES 2018}.
		\item HoloFlight – 3D Real-time flight data tracking and representation. Was showcased at Unite India 2017.
	\end{ecvitemize}
}

\vspace{8pt}
\ecvsection{Education And Training}

\ecvtitle[12pt]{May 2010 - Apr 2014}{Bachelor of Technology in Computer Science}
\ecvitem[2pt]{}{Govt. Model Engineering College, Kochi}

\newpage

\ecvsection{Personal Skills}

\ecvmothertongue{Malayalam}
\ecvlanguageheader
\ecvlanguage{English}{C2}{C2}{C1}{C1}{C1}
\ecvlastlanguage{Hindi}{B2}{B2}{B1}{B1}{A2}
\ecvlanguagefooter

\vspace{10pt}

\ecvblueitem[10pt]{Job-related skills}{
	\begin{ecvitemize}
		\item Expertise in both C\# and C++ (Wrote critical parts in both managed and unmanaged code for multiple projects).
		\item Proficient in working with remote teams (Most of the project team is situated in Germany and Seattle).
		\item Ability to discover, research and port libraries (Made extensive use of open source libraries due to small sized team).
		\item Experience with source control systems (Uses Git and Visual Studio Team Services at an advanced level).
	\end{ecvitemize}
}

\ecvblueitem[10pt]{Organisational / managerial skills}{
	\begin{ecvitemize}
		\item Vice chairman of entrepreneurship cell during college.
		\item Member in executive committee of technical festival during college.
	\end{ecvitemize}
}

\ecvblueitem[10pt]{Other skills}{
	\begin{ecvitemize}
		\item Intermediate level knowledge in Photoshop (Design team member of college magazine).
		\item Beginner level knowledge in 3DS Max (3D model optimization for some projects).
	\end{ecvitemize}
}

\ecvdigitalcompetence
	{\ecvProficient}
	{\ecvProficient}
	{\ecvIndependent}
	{\ecvProficient}
	{\ecvProficient}

\vspace{10pt}
\ecvsection{Additional Information}

\ecvblueitem[10pt]{Certifications}{Unity Certified Developer (November 2017 - Present)}

\end{europasscv}
\end{document} 